Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-01 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Opinionated framework
More
Users

\section{HC  IEC Framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
The framework is a reusable architectural design together with an implementation \cite{campbell1991choices}, 
providing generalized components to developers of IEC systems. In the description we deliberately use the more general term Human instead of User, because humans are not always playing the role of users in software engineering sense, they could just be interacting naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. The framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary process in a given IEC application.

>>>>

\section{HC  IEC Framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
The framework is a reusable architectural design together with an implementation \cite{campbell1991choices}, 
providing generalized components to developers of IEC systems. In the description we deliberately use the more general 
term Human instead of User, because humans are not always playing the role of users in software engineering sense, they
could just be interacting naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. The framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary process in a given IEC application. Software frameworks often have a vison or a way of thinking \cite{carneiro2010introducing} guiding their
design. Before entering to details the main design decisions of the framework are explained next:

\begin{itemize}
\item {\bf Users are Human} 
  The user will have certain goals and has the intention to perform certain tasks.
  The framework follows the approach of human centered computing \cite{sebe2010human},
  in which the context, environment, interfaces, preferences, accessibility, human relations, cognitive
  limitations, culture, creativity and other human aspects are an integral part of the system.

\item {\bf Users are not alone}
  Relationship between users in an interactive evolutionary algorithm can also be modeled 
  as a social network, with well established semantics, algorithms and metrics \cite{ahuja1993network}.
  A graph model could enable researchers to find other ways of identifying leaders of 
  opinion or measuring the similarity between user's preferences. 
  These measures can then be used by recommender algorithms selecting 
  phenotypes according users' preferences.

\item {\bf Context of use matters}
 The product will  be used within a certain range of technical, physical and social or
 organizational environments \cite{maguire2001context} that may affect its use.
 We can refer to these environments as the \textit{context of use} (see
 Figure \ref{fig:logicalmodel}), this concept has been formally defined
 by ISO standard 9241-11 \cite{international1998iso} as \textit{``users,
 tasks and equipment (hardware, software and materials), and the
 physical and social environments in which a product is used"}. \\ 
 In daily life we often find products that are difficult to use or
 understand. This type of difficulties are \textit{usability problems}
 that arise from  diverse issues that have not been addressed in the
 design of the product's \textit{user-artifact interaction}.

\item {\bf Interaction is a stream of actions}

\item {\bf Users are volunteers}

\item {\bf Solutions could be: real objects, processes, digital artifacts}

\end{itemize}
